\normalfont\textbf{ \Large {Reducing data traffic in wireless structural health monitoring systems using embedded computing}}

### 2015-02-10 Paper/PaperJahrSchlichSHM.tex
summary

\author
{\large Katrin Jahr, Robert Schlich\\
\\
\normalsize{Degree program “Civil Engineering” (M.Sc.)}\\
\normalsize{Bauhaus-Universität Weimar, Germany}\\
\\
\normalsize{katrin.jahr@uni-weimar.de, }
\normalsize{robert.schlich@uni-weimar.de}
}

@@

\section*{Design and implementation of the wireless structural health monitoring system}
In the following section, the wireless structural health monitoring system is introduced and the software implementation is described.
The wireless SHM system consists of wireless sensor nodes and a host computer, linked with a basestation.
The sensor nodes and the basestation are of type "Oracle Sun SPOT". 
The Sun SPOTS are equipped with several components, see \autoref{fig:SPOT}.
Among others, the sensor board includes an accelerometer and eight independent RGB-LEDs.
The 3-axis digital output accelerometer with sensitivity ranging between $\pm$\,2\,g and $\pm$\,8\,g has a maximum sampling rate of 125Hz \citep{eDemo2010}.

@@

\begin{itemize}
	\item data traffic was reduced by XX\,\% 
\end{itemize}

>>>>

\author
{\large Katrin Jahr, Robert Schlich\\
\\
\normalsize{Degree program “Civil Engineering” (M.Sc.)}\\
\normalsize{Bauhaus-Universität Weimar, Germany}\\
\\
\normalsize{katrin.jahr@uni-weimar.de \qquad}
\normalsize{robert.schlich@uni-weimar.de}
}

@@

\section*{Design and implementation of the wireless structural health monitoring system}
In the following section, the wireless structural health monitoring system is introduced and the software implementation is described.
The wireless SHM system consists of wireless sensor nodes and a host computer, linked with a basestation.
The sensor nodes and the basestation are of type "Oracle Sun SPOT". 
The Sun SPOTS are equipped with several components, see \autoref{fig:SPOT}.
Among others, the sensor board includes an accelerometer and eight independent RGB-LEDs.
The 3-axis digital output accelerometer with sensitivity ranging between $\pm$\,2\,g and $\pm$\,8\,g has a maximum sampling rate of 125\,Hz \citep{eDemo2010}.

@@

In structural health monitoring, a decentralized data compression stragegy reduces data traffic and storage space.
Using a fast Fourier transform to determine the natural frequency allows conclusions about the structural integrity of a structure.
The transmitted data was reduced exponentially, saving up to xx MB per sampling event.
